An algorithm for the optimization of finite element integration loops

### 2016-03-21 TOMS_Paper/assembly.tex
fix grant numbers

This research is partly funded by the MAPDES project, by the
Department of Computing at Imperial College London, by EPSRC through
grants EP/I00677X/1, EP/I006761/1, and EP/L000407/1, by NERC grants
NE/K008951/1 and NE/K006789/1, by the U.S.  National Science
Foundation through grants 0811457 and 0926687, by the U.S. Army
through contract W911NF-10-1-000, and by a HiPEAC collaboration
grant. The authors would like to thank Mr. Andrew T.T. McRae,
Dr. Lawrence Mitchell, and Dr. Francis Russell for their invaluable
suggestions and their contribution to the Firedrake project.

Author's addresses: Fabio Luporini $\&$ Paul H. J. Kelly, Department of Computing,
Imperial College London; David A. Ham, Department of Computing and
Department of Mathematics, Imperial College London; 
\end{bottomstuff}

>>>>

This work was supported by by the
Department of Computing at Imperial College London, the Engineering and
Physical Sciences Research Council [grant number EP/L000407/1], and the Natural
Environment Research Council [grant numbers 
NE/K008951/1 and NE/K006789/1], and by a HiPEAC collaboration
grant. The authors would like to thank Mr. Andrew T.T. McRae,
Dr. Lawrence Mitchell, and Dr. Francis Russell for their invaluable
suggestions and their contribution to the Firedrake project.

Author's addresses: Fabio Luporini $\&$ Paul H. J. Kelly, Department of Computing,
Imperial College London; David A. Ham, Department of Mathematics, Imperial College London; 
\end{bottomstuff}
